---
title: "Shiny Presentation"
author: "Samuel Pinkava"
date: "September 15, 2018"
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

##Shiny Project

This Shiny app will place random markers around various cities around the world.

Select the city from the dropdown menu and then click on "New Points." You will
then get a map of random points from around that city.

##Baltimore

Suppose you want to randomly place geocaches around Baltimore.

```{r}
library(leaflet)

r_colors <- rgb(t(col2rgb(colors()) / 255))
names(r_colors) <- colors()

points <- cbind(rnorm(10)/4 - 76.6122, rnorm(10)/8 + 39.2904)

p <-leaflet() %>%
      addProviderTiles(providers$Stamen.TonerLite,
        options = providerTileOptions(noWrap = TRUE)
      ) %>%
      addMarkers(lng = points[,1],lat = points[,2])
p
```

##London

You can set up corner shops randomly around London.

```{r}
library(leaflet)

r_colors <- rgb(t(col2rgb(colors()) / 255))
names(r_colors) <- colors()

points <- cbind(rnorm(10)/4 - 0.1278, rnorm(10)/8 + 51.5074)

p <-leaflet() %>%
      addProviderTiles(providers$Stamen.TonerLite,
        options = providerTileOptions(noWrap = TRUE)
      ) %>%
      addMarkers(lng = points[,1],lat = points[,2])
p
```

##Kathmandu

You may want to create random camp sites around Kathmandu.

```{r}
library(leaflet)

r_colors <- rgb(t(col2rgb(colors()) / 255))
names(r_colors) <- colors()

points <- cbind(rnorm(10)/4 + 85.3240, rnorm(10)/8 + 27.7172)

p <-leaflet() %>%
      addProviderTiles(providers$Stamen.TonerLite,
        options = providerTileOptions(noWrap = TRUE)
      ) %>%
      addMarkers(lng = points[,1],lat = points[,2])
p
```
