---
title: "Shiny Project"
author: "Samuel Pinkava"
date: "September 1, 2018"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

## Shiny Project

This Shiny app will place random markers around various cities around the world.

Select the city from the dropdown menu and then click on "New Points." You will
then get a map of random points from around that city.

## Baltimore
Suppose you want to randomly place geocaches around Baltimore.

```{r}
library(shiny)
library(leaflet)

r_colors <- rgb(t(col2rgb(colors()) / 255))
names(r_colors) <- colors()

ui <- fluidPage(
  leafletOutput("mymap"),
  p(),
  actionButton("recalc", "New points")
)

server <- function(input, output, session) {

  points <- eventReactive(input$recalc, {
    cbind(rnorm(10)/4 - 76.6122, rnorm(10)/8 + 39.2904)
  }, ignoreNULL = FALSE)

  output$mymap <- renderLeaflet({
    leaflet() %>%
      addProviderTiles(providers$Stamen.TonerLite,
        options = providerTileOptions(noWrap = TRUE)
      ) %>%
      addMarkers(data = points())
  })
}

shinyApp(ui, server)
```

## London

You can set up corner shops randomly around London.

```{r}
library(shiny)
library(leaflet)

r_colors <- rgb(t(col2rgb(colors()) / 255))
names(r_colors) <- colors()

ui <- fluidPage(
  leafletOutput("mymap"),
  p(),
  actionButton("recalc", "New points")
)

server <- function(input, output, session) {

  points <- eventReactive(input$recalc, {
    cbind(rnorm(10)/4 - 0.1278, rnorm(10)/8 + 51.5074)
  }, ignoreNULL = FALSE)

  output$mymap <- renderLeaflet({
    leaflet() %>%
      addProviderTiles(providers$Stamen.TonerLite,
        options = providerTileOptions(noWrap = TRUE)
      ) %>%
      addMarkers(data = points())
  })
}

shinyApp(ui, server)
```

##Kathmandu

You may want to create random camp sites around Kathmandu.

```{r}
library(shiny)
library(leaflet)

r_colors <- rgb(t(col2rgb(colors()) / 255))
names(r_colors) <- colors()

ui <- fluidPage(
  leafletOutput("mymap"),
  p(),
  actionButton("recalc", "New points")
)

server <- function(input, output, session) {

  points <- eventReactive(input$recalc, {
    cbind(rnorm(10)/4 + 85.3240, rnorm(10)/8 + 27.7172)
  }, ignoreNULL = FALSE)

  output$mymap <- renderLeaflet({
    leaflet() %>%
      addProviderTiles(providers$Stamen.TonerLite,
        options = providerTileOptions(noWrap = TRUE)
      ) %>%
      addMarkers(data = points())
  })
}

shinyApp(ui, server)
```

